DataGatheringandAnalysis

### 2014-11-13 GEMDataSource.Rmd
New data for opportunities
Updated environment and regression eq

# Import GEM perceived opportunities data as a proxy for potential control variables
PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedOpportunities.csv", header = TRUE, cache = FALSE)

@@

# Check data to confirm change
summary(FinalGEM)

# Run a linear regression
R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear, data = FinalGEM)
summary(R1)

@@

# Plot graph
car::scatterplotMatrix(FinalGEM)

# Merge GDPGrowth and FinalMerge
CompeteDataset <- merge(FinalGEM, GDPGrowth,
                   union("Country", "Year"),
                   all = TRUE)

>>>>

# Import GEM perceived opportunities data as a proxy for potential control variables
PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE)

@@

# Merge GDPGrowth and FinalGEM
CompleteDataset <- merge(FinalGEM, GDPGrowth,
                   union("Country", "Year"),
                   all = TRUE)

# Remove unncessary data from environment
remove(CCurrentOwner, CEntreIntention, CFearFail, CNascentEntre, CPerceivedCapabilities, CPerceivedOpportunities, CurrentOwner, EntreIntention, FearFail, MergedGEM, MergedGem2, MergedGem3, MergedGem4, PerceivedCapabilities, PerceivedOpportunities, NascentEntre)

# Check data to confirm change
summary(CompleteDataset)

# Run a linear regression
R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear + AnnualGDPGrowth + 
           PercentOpportunities, data = CompleteDataset)
summary(R1)

@@

# Plot graph
car::scatterplotMatrix(CompleteDataset)
